\section{A LITTLE BIT OF HISTORY}

Through mostly oral history, a few most recent and memorable facts are passed along, some say to honor those who died, some say so we never repeat the same mistakes. These are those stories:

\begin{itemize}
	\item \textbf{First Battle of the Hoover Dam:} since first estabilishing themselves, the NCR always had a tenuous presence in the Mojave. Between the difficulty in estabilishing supply lines, raider troubles and the resistance from Mr. House and the Families, they already had their hands full. However, things got much worse when the conqueror known as Caesar got interested on the region. Between skirmishes and sabotage from the Frumentarii, NCR forces were seriously depleted. This culminated in an all-out assault by Legion forces under Malpais Legate, a direct hit on Hoover Dam. When Gen. Lee Oliver ordered his troops to retreat to the middle of the dam, the Legate ordered the Legion to keep increasing pressure. However, the NCR stand on the dam proved impenetrable, and along with the snipers, decimated the Legion troops, who retreated to the Fort and Cottonwood Cove. For his failure, Legate Joshua Graham fell in disgraced, was covered in tar, burned alive and thrown into the Grand Canyon. 
	
	\item \textbf{Second Battle of Hoover Dam:} still present and still strong in the Mojave, Caesar himself came to lead his forces to ultimate victory. However, this conflict had a third party that eventually held the result of this battle in the palm of his hands. Having met both forces, both leaders, the third power known as The Courier and his many allies, like Boomers, the Great Khans, and some say that even a small but powerful contingent of former Enclave soldiers, tipped the balance of power and helped NCR to remove Legion presence for good. However, like most endeavours, there are signs that this one was not as successfull as they'd hoped.
	
	\item \textbf{Pacification of the Three Tribes}: before the war, Mr. House made preparations to prevent that Las Vegas would be hit by missile strikes. After the war, Vegas stood tall, mostly untouched by the devastation around it. Upon detecting the first NCR scouts, House realized that he would need help to keep his control over the region. To that end, he contacted three tribes: \textbf{the Mojave Boot-Riders}, a mighty violent tribe of hunters that would become the Chairmen; \textbf{the Slither Kin}, a tribe whose preferred tactics of deception, luring their victims and backstabbing them, became the Omertas; and \textbf{third, unidentified tribe} of cannibals became the White Glove Society, elitist snobs who mostly act like they have abandoned their old ways, along with their old name. To each family, House assigned a casino, hotel, and other attractions on New Vegas. This deal seems to have been renewed with the Courier upon taking over the strip.
	
	\item \textbf{Massacre of Bitter Springs:} even among the many mistakes commited by the NCR, the Massacre deserves special mention. In 2278, NCR troops surrounded a Great Khans camp at Bitter Springs, a camp their intel told was full of raiders. When elderly, women and children started fleeing the camp, the snipers from First Recon radioed command to confirm their orders. A miscommunication led to the snipers killing until they ran out of ammunition. After that day, the surviving Khans retreated to Red Rock Canyon, with many members becoming broken in many ways due to the trauma. On the NCR side, there is a lowkey effort to throw this under wraps, but sweeping away something of this magnitude would prove to be impossible. To this day, graffiti of the words "REMEMBER BITTER SPRINGS" pop up in random places around New Vegas, a mark of shame that the NCR will never be able to wash away.
	
	\item \textbf{Operation Sunburst:} this was the defeat that have consolidated the Brotherhood of Steel as a minor power in New Vegas. Elder Elijah, leader of this Brotherhood chapter, was obsessed with discovering the technology and the great weapon that was said to be hidden in the HELIOS ONE Power Station, something called Archimedes. The  base, however, proved to be a poorly defensible position, and when NCR troopers attacked, Brotherhood forces were overwhelmed by their numbers. Elijah fled, leaving his post as Elder and his followers behind, and Elder McNamara took over and quickly organized a retreat to Hidden Valley. However, by then, about half of the Brotherhood's forces were killed, with the NCR taking over their equipment and power armor, and taking over their place in searching for Archimedes.
	
	\item \textbf{Massacre of Nipton:} Nipton was something of a neutral zone, where for the right amount of caps, NCR troopers, legionnaires, raiders and all could enjoy the gambling and prostitution that the city offered. In 2281, as a demonstration of power, Legion soldiers, to show their power, destroyed the city and killed nearly everyone present, using a lottery system. The grand winner, a Powder Ganger, was allowed to leave alive, though some say that he was killed when leaving the city. The second place was allowed to live, but not to leave, as his legs were destroyed. Others were either enslaved, crucified or decapitated, the heads placed on the tips of spears, firm on the ground, a warning of the fate that awaited the rest of the Mojave.
	
	\item \textbf{Searchlight Disaster:} probably the most successfull attack from the Legion, Searchlight was a small town where, pre war, nuclear waste was being stored for disposal. Word of this reached Legion troops, who deployed a small  that detonated the still active nuclear waste. The result is one of the most radiactive places in the Mojave, where only ghouls could thrive. In 2282, a group of ghouls commanded by Jason Bright estabilished the first ghoul settlement on that place, counting on the radiation to keep smoothskins out.
	
	\item \textbf{The Twin Bombs:} this one is spoken mostly as a legend, of when two couriers, one chasing the other, crossed the Divide, a radioactive hellscape recently destroyed by atomic fire. Legend tells that one of those was The Courier, who went after their past, and met with it in the figure of another, a man some called Ulysses. It is unknown if they ended as friends, foes or vanquisher and vanquished, but after the day of the combat, two encampents, near NCR Outpost and Cottowood Cove, were hit by atomic bombs, decimating most of the armies, and closing the I-15. Folks say that thanks to this action, the Second Battle of Hoover Damn was a much smaller conflict than it could have been, though none agree on if it that's a good or a bad thing.
\end{itemize}
