\section{INTRODUCTION}

\epigraph{\textit{I planned each charted course \\
Each careful step along the byway \\
And more, much, much more \\
I did it, I did it my way}}{\textit{``My Way'', Frank Sinatra}}

War. War never changes. The year is 2270. In the Mojave desert, the New California Republic spreads its influence. After a deal with Robert House, famed millionaire and owner of the most mysterious casino in New Vegas, the Lucky 38, the NCR starts settlements, fights off raiders, and seems to do a good job in bringing civilization to the desert for several years, even restarting Hoover Dam and increasing electricity supply to New Vegas. Then, the Legion arrived.

The year is 2277. Coming from Arizona, Caesar's Legion starts to move into the Mojave, starting by Fortification Hill, where they set their camp. Soon, under command of Legate Joshua Graham, the Legion moves to take over Hoover Dam. After an initial victory, the NCR lures the Graham to a trap, causing them to retreat. Humiliated, Caesar orders that Graham be coated in pitch, lit on fire and thrown into the Grand Canyon, to serve as an example. 

The year is 2281. The Mojave is largely under the influence of the NCR, but the Legion has started expanding. The town of Nipton, a hub of thievery and prostitution, is destroyed as a both a demonstration of power and as a way to send a moralizing message to New Vegas. The NCR begins to feel the weigth of the conflict, and people slowly begin to notice this. A new battle for Hoover Dam seems inevitable. 

From all over New Vegas, stories begin to crop up about a person who came back from the dead for revenge, in the small town of Goodspring. Very little is known about this person, except that they are called Courier Six. Along the way, this person helped a lot of people, restoring order and eliminating various threats to the citizens of the Mojave, accruing a reputation of being something of a Messiah. His actions tip the balance in favor of the NCR, and in the coming battle, his help is decisive in assuring the victory of the NCR.

The year is 2286, five years after final battle between NCR and Caesar's Legions. The Mojave is a changed place. The Great Khans stopped supplying chems to other factions, reconnecting to the Followers of the Apocalypse. The Brotherhood of Steel patrolled part of the desert, NCR handled the other. New Vegas poorest neighborhoods, Westside and Freeside, began to flourish. Although troubled by the taxes, NCR citizens experienced prosperity like never before. Caesar's Legion was no more.

That's where we begin.

\newpage
Or not. It's your adventure, after all.