
\subsection{PERKS}
\begin{longtable}{|p{3.3cm}|p{3.1cm}|p{1.2cm}|p{8.4cm}|}
\hline
\bfseries Name & \bfseries Other reqs & \bfseries Ranks & \bfseries Description \\
\hline
\endhead

Action Boy / Action Girl & AG 6 & 2 & Rank 1: +1 AG Rank 2: +1 AG +1 ST \\
Adamantium Skeleton & & 1 & Only cripple limbs on critical \\
Animal Friend & CH 6, Survival 45 & 2 & Rank 1: hostile animals become friendly Rank 2: they come to your aid against enemies except against other animals. \\
Better Criticals & PE 6, LK 6 & 1 & + 3d6 damage with critical hits. \\
Black Widow / Lady Killer & & 1 & + 2d6 damage to the opposite sex and positive reaction on all except negative critical \\
Cannibal & & 1 & Y ou can eat a human corpse to regain hit points, but lose reputation if witnessed \\
Center of Mass & Guns 70 & 1 & In Aimed Shots, you do an additional +1d 20 damage when targeting the torso. \\
Chem Resistant & Medicine 60 & 1 & Half as likely to get addicted. \\
Chemist & Medicine 60 & 1 & Chems last twice as long, stimpacks heal an additional 100 HP. \\
Cherchez La Femme / Confirmed Bachelor & & 1 & + 2d6 damage to the same sex and positive reaction on all except negative critical \\
Commando & & 1 & +25\% accuracy in Aimed Shots with two-handed weapons. \\
Comprehension & IN 4 & 1 & You gain one additional skill point for reading books and double the skill points for reading magazines. \\
Computer Whiz & IN 7, Science 70 & 1 & Can make one extra attempt to hack a locked-down terminal. \\
Cowboy & Guns 45, Melee 45 & 1 & + 2d6 damage done by dynamite, hatchets, knives, revolvers, and lever-action guns. \\
Demolition Expert & Explosives 50 & 3 & + 2d6 damage with explosives. \\
Educated & IN 4 & 1 & You gain two more skill points every time you advance in level. \\
Entomologist & IN 4, Survival 45 & 1 & You do an additional 3d6 damage every time you attack a mutated insect. \\
Fast Metabolism & & 1 & + 4d6 Hit Points restored with stimpaks. \\
Ghastly Scavenger & Cannibal perk & 1 & Y ou can eat a super mutant or ghoul corpse to regain hit points, but lose reputation if witnessed \\
Gunslinger & & 1 & +25\% accuracy in Aimed Shots with one-handed weapons. \\
Hit the Deck & Explosives 70 & 1 & +25 DT against explosives. \\
Hunter & Survival 30 & 1 & In combat, you do 4d6 more critical damage against animals and mutated animals. \\
Intense Training & & 10 & You can put a single point into any of your SPECIAL attributes. \\
Laser Commander & Energy Weapons 90 & 1 & You do an extra 2d6 damage and have a 20\% extra chance to critically hit with any laser weapon. \\
Lead Belly & EN 5 & 1 & -50\% Rads taken from food and water sources. \\
Life Giver & EN 6 & 1 & + 6 0 hit points. \\
Light Step & PE 6, AG 6 & 1 & Floor traps or mines will not be set off. \\
Meltdown & Energy Weapons 90 & 1 & Foes killed by your Energy Weapons emit a corona of harmful energy, causing 1d6 of damage to characters nearby \\
Miss Fortune & LK 6 & 1 & Whenever engaging a new target in combat, roll a Luck check. On success, Miss Fortune will appear and kill the target, then disappear. There is no way to interact with Miss Fortune. \\
Mister Sandman & Sneak 60 & 1 & Can instantly kill a sleeping non-player character and earn bonus XP when doing so. \\
Mysterious Stranger & LK 6 & 1 & Whenever engaging a new target in combat, roll a Luck check. On success, the Stranger will appear and kill the target, then disappear. There is no way to interact with the Stranger. \\
Nerd Rage! & IN 5, Science 50 & 1 & +15 DT and ST increased to 10 whenever health is 20\% or lower. \\
Ninja & Melee Weapons 80, Sneak 80 & 1 & +30\% critical damage chance with unarmed attacks, melee or silenced weapons, +25\% damage, rounded up, with melee/unarmed sneak attack criticals. \\
Pack Rat & IN 5, Barter 70 & 1 & Items with a weight of two pounds or less now weigh nothing . \\
Paralyzing Palm & Unarmed 70 & 1 & Can paralyze an enemy for 2 turns with an Unarmed Aimed Shot \\
Piercing Strike & Unarmed 70 & 1 & All your unarmed and melee attacks negate 15 points of DT. \\
Plasma Spaz & Energy Weapons 70 & 1 & You get two Action Points exclusively for use with plasma weapons each turn \\
Purifier & & 1 & You do 3d20 extra damage with melee and unarmed weapons against centaurs, night stalkers, spore plants, spore carriers, deathclaws and super mutants. \\
Pyromaniac & Explosives 60 & 1 & +4d6 damage with fire-based weapons. \\
Quick Draw & AG 5 & 1 & +2 to Sequence \\
Rad Child & Survival 70 & 1 & Instead of dying, go into a regenerative coma for the 5 turns that regenerates the 1/5th of rads in health \\
Rad Resistance & EN 5, Survival 40 & 1 & +25\% Rads resistance permanently. \\
Rapid Reload & AG 5, Guns 30 & 1 & Don’t need to take an action to reload \\
Robotics Expert & Science 50 & 1 & +3d6 damage to robots; can shut down robots by sneaking up on them and deactivating \\
Shotgun Surgeon & Guns 45 & 1 & When using shotguns, regardless of ammunition used, you ignore an additional 10 points of a target's Damage Threshold \\
Silent Running & AG 6, Sneak 50 & 1 & Running no longer factors into a successful sneak attempt \\
Slayer & ST 7, AG 7, Unarmed 90 & 1 & Get one extra action when using melee or unarmed attacks \\
Sniper & PE 6, AG 6 & 1 & 25\% more likely to hit the target's head with Aimed Shots \\
Stonewall & ST 6, EN 6 & 1 & +5 DT against melee and unarmed attacks and cannot be knocked down during combat. \\
Strong Back & ST 5, EN 5 & 1 & +50 Carry Weight. \\
Tag! & & 1 & Fourth ``tag'' skill: +15 points to that skill. \\
Terrifying Presence & Speech 70 & 1 & +2d6 when trying to intimidate a character through dialogue . \\
The Professional & Sneak 70 & 1 & Your sneak attack criticals with revolvers, pistols, and submachine guns (guns and energy weapons) all inflict an additional 20\% damage. \\
Toughness & EN 5 & 2 & +3 DT permanently. \\
Unstoppable Force & ST 7, Melee Weapons 90 & 1 & x4 normal damage through enemy blocks with melee and unarmed attacks. \\
Weapon Handling & ST $<$ 10 & 1 & Weapon ST requirements are now 2 points lower than normal for you. \\

\hline
\end{longtable}
